Epidemiological Data Analysis

### 2023-06-20 analysis/epi_analysis.Rmd
minor update line list data

```{r}
line_list_dat <- epi_data_ll %>%
  filter(respiratory_infection == "yes") %>%
  dplyr::select(class, date_symptom, date_absent, date_back) %>%
  as.matrix() %>%
  xtable::xtable()

>>>>

```{r}
line_list_dat <- epi_data_ll %>%
  filter(respiratory_infection == "yes") %>%
  dplyr::select(class, date_symptom, date_absent, date_back) %>%
  arrange(class, date_absent) %>%
  as.matrix() %>%
  xtable::xtable()
